---
title: "GameFun - AB testing analysis"
author: "vincy hu"
date: "5/19/2020"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 2
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#library(devtools)
#install_github('yihui/tinytex')
```

---------------------------------------------------------------------------------------------------

# Import the Data

```{r}
library(readxl)
library(tidyverse)
library(dplyr)
gf <- read_excel('GameFun.xlsx')
summary(gf)
```
First, insert and exlore the dataset a little bit
(The first column is the anonymized customer id. The second column, “test”, indicates whether the user was part of the treatment group (test =1) or the control group (test=0). There are three demographic variables, “gender” (male =1, female =0), “income” (this is measured in thousands), and “gamer” (gamer = 1, if user is a gaming enthusiast; 0, otherwise). The website that a customer visited is in the variable “site”. The variable “impressions” contains the number of advertising impressions that a customer received. If a customer is in the test group, then all of this customer’s impressions are for the Game-Fun’s ad; if a customer is in the control group, then all of this customer’s impressions are for the irrelevant ad. Last, the column “purchase” is the dependent variable, and it indicates if the customer purchased anything within 30 days after her/his conversation to the game (30 days is the expected customer lifetime duration for a mobile gamer).)





# Question one
Before evaluating the effect of an experiment, it is important to make sure that the
experiment was executed correctly. Check whether the test and control groups are
probabilistically equivalent on their observables?

## 1a
More specific, compare the averages of the income, gender and gamer variables
in the test and control groups. You should also report the % difference in the
averages. Compute its statistical significance

```{r}
# first, we split the control and test group by the test column.
cont <- filter(gf,gf$test == '0')
exp <- filter(gf,gf$test == '1')

###################### 1a #######################
# 1. test for mean of income between control and experiment. using two-sample t-test
(mean(cont$income) - mean(exp$income))  # the diffenrence of income is $0.2277

var.test(cont$income, exp$income, ratio = 1, alternative = "two.sided")
# pvalue = 0.505, we don't have enough evidence to reject that two variances are equal
t.test(cont$income, exp$income, alternative = "two.sided", mu = 0, paired = FALSE, var.equal = TRUE)
# p = 0.1284, so wwe don't have enough evidence to reject that two means are equal
# Thus we can conclude that income level of control and experiment group are comparable.


# 2. test for proportion of gender between control and experiment. using two-sample proportion test
mean(cont$gender) - mean(exp$gender)  # the diffenrence of proportion of male is 0.06%

table(cont$gender)

table(exp$gender)

prop.test(c(18183,7747), c(9908+18183,4210+7747), alternative = "two.sided", correct = FALSE)
# p = 0.90, so wwe don't have enough evidence to reject that male proportions are equal
# Thus we can conclude that gender proportion of control and experiment group are comparable.

# 3. test for proportion of gamer between control and experiment. using two-sample proportion test
mean(cont$gamer) - mean(exp$gamer)  # the diffenrence of proportion of male is 0.049%

table(cont$gamer)

table(exp$gamer)

prop.test(c(7196,16892), c(7196+4761,16892+11199), alternative = "two.sided", correct = FALSE)
# p = 0.93, so wwe don't have enough evidence to reject that gamer proportions are equal
# Thus we can conclude that gamer proportion of control and experiment group are comparable.

```

# 2a
```{r}

all_cont <- mean(cont$purchase)
all_cont
all_exp <- mean(exp$purchase)
all_exp
all_exp-all_cont # 4% higher purchase rate in exp group

var.test(cont$purchase, exp$purchase, ratio = 1, alternative = "two.sided") #variance not equal

t.test(cont$purchase, exp$purchase, alternative = "two.sided", mu = 0, paired = FALSE, var.equal = FALSE)

# the differenct is significant


```

#2b
```{r}
# for Male

Male_cont <- nrow(filter(cont,cont$gender =='1' & cont$purchase == '1'))/nrow(filter(cont,cont$gender =='1'))
Male_cont 
Male_exp <- nrow(filter(exp,exp$gender == '1'& exp$purchase == '1'))/nrow(filter(exp,exp$gender == '1'))
Male_exp 
Male_exp - Male_cont # male purchase rate in experiment group is 3.7% higher than the rate in male control group

# for FeMale

FeMale_cont <- nrow(filter(cont,cont$gender =='0' & cont$purchase == '1'))/nrow(filter(cont,control$gender =='0'))
FeMale_cont
FeMale_exp <- nrow(filter(exp,exp$gender == '0'& exp$purchase == '1'))/nrow(filter(exp,exp$gender == '0'))
FeMale_exp
FeMale_exp-FeMale_cont  # female purchase rate in experiment group is 4.65% higher than the rate in male control group


# significance test - male
Male_cont <- filter(cont,cont$gender =='1')
Male_exp <- filter(exp,exp$gender =='1')

table(Male_cont$purchase)
table(Male_exp$purchase)

prop.test(c(1356,288), c(1356+16827,288+7459), alternative = "two.sided", correct = FALSE)
# the difference is significant for male exp group


# significance test - male
Female_cont <- filter(cont,cont$gender =='0')
Female_exp <- filter(exp,exp$gender =='0')

table(Female_cont$purchase)
table(Female_exp$purchase)

prop.test(c(802,145), c(802+9106,145+4065), alternative = "two.sided", correct = FALSE)
# the difference is significant in female exp group
```

#2c.
```{r}
# for Gamer

gamer_cont <- nrow(filter(cont,cont$gamer =='1' & cont$purchase == '1'))/nrow(filter(cont,cont$gamer =='1'))
gamer_cont
gamer_exp <- nrow(filter(exp,exp$gamer == '1'& exp$purchase == '1'))/nrow(filter(exp,exp$gamer == '1'))
gamer_exp
gamer_exp - gamer_cont # male purchase rate in experiment group is 6.9% higher than the rate in male control group

# for nongamer

nongamer_cont <- nrow(filter(cont,cont$gamer =='0' & cont$purchase == '1'))/nrow(filter(cont,control$gamer =='0'))
nongamer_cont
nongamer_exp <- nrow(filter(exp,exp$gamer == '0'& exp$purchase == '1'))/nrow(filter(exp,exp$gamer == '0'))
nongamer_exp
nongamer_exp - nongamer_cont  # female purchase rate in experiment group is 0.23% lower than the rate in male control group


# significance test - gamer
gamer_cont <- filter(cont,cont$gamer =='1')
gamer_exp <- filter(exp,exp$gamer =='1')

table(gamer_cont$purchase)
table(gamer_exp$purchase)

prop.test(c(1765,255), c(1765+15127,255+6941), alternative = "two.sided", correct = FALSE)
# the difference is significant for gamer exp group


# significance test - nongamer
gamer_cont <- filter(cont,cont$gamer =='0')
gamer_exp <- filter(exp,exp$gamer =='0')

table(gamer_cont$purchase)
table(gamer_exp$purchase)

prop.test(c(393,178), c(393+10806,178+4583), alternative = "two.sided", correct = FALSE)
# the difference is not significant in nongamer exp group
```

#2d
```{r}

# for male Gamer

malegamer_cont <- nrow(filter(cont,cont$gamer =='1' & cont$purchase == '1' & cont$gender == "1"))/nrow(filter(cont,cont$gamer =='1'& cont$gender == "1"))
malegamer_cont
malegamer_exp <- nrow(filter(exp,exp$gamer =='1' & exp$purchase == '1' & exp$gender == "1"))/nrow(filter(exp,exp$gamer =='1'& exp$gender == "1"))
malegamer_exp
malegamer_exp - malegamer_cont # male purchase rate in experiment group is 6.4% higher than the rate in male control group

# for female gamer

femalegamer_cont <- nrow(filter(cont,cont$gamer =='1' & cont$purchase == '1' & cont$gender == "0"))/nrow(filter(cont,control$gamer =='1'&cont$gender == "0"))
femalegamer_cont
femalegamer_exp <- nrow(filter(exp,exp$gamer == '1'& exp$purchase == '1'& exp$gender == "0"))/nrow(filter(exp,exp$gamer == '1'&exp$gender == "0"))
femalegamer_exp
femalegamer_exp - femalegamer_cont  # female purchase rate in experiment group is 7.8% lower than the rate in male control group


# significance test - malegamer
malegamer_cont <- filter(cont,cont$gamer =='1'&cont$gender=="1")
malegamer_exp <- filter(exp,exp$gamer =='1'&exp$gender=="1")

table(malegamer_cont$purchase)
table(malegamer_exp$purchase)

prop.test(c(1105,174), c(1105+9792,174+4494), alternative = "two.sided", correct = FALSE)
# the difference is significant for male gamer exp group


# significance test - femalegamer
femalegamer_cont <- filter(cont,cont$gamer =='0'&cont$gender=="0")
femalegamer_exp <- filter(exp,exp$gender=="0")

table(gamer_cont$purchase)
table(gamer_exp$purchase)

prop.test(c(393,178), c(393+10806,178+4583), alternative = "two.sided", correct = FALSE)
# the difference is not significant in female gamer exp group

```


#3 
```{r}
# 3a
cont_rev <- mean(cont$purchase)*37.5
exp_rev <- mean(exp$purchase)*12.5
cont_rev
exp_rev


# 3b
# male gamer revenue 
malegamer_Cont_Rev <- nrow(filter(cont,cont$gamer =='1' & cont$purchase == '1' & cont$gender == "1"))/nrow(filter(cont,cont$gamer =='1'& cont$gender == "1"))*37.5
malegamer_Exp_Rev <- nrow(filter(exp,exp$gamer =='1' & exp$purchase == '1' & exp$gender == "1"))/nrow(filter(exp,exp$gamer =='1'& exp$gender == "1"))*12.5

malegamer_Cont_Rev
malegamer_Exp_Rev


#female gamer revenue
femalegamer_Cont_Rev <- nrow(filter(cont,cont$gamer =='1' & cont$purchase == '1' & cont$gender == "0"))/nrow(filter(cont,cont$gamer =='1'& cont$gender == "0"))*37.5
femalegamer_Exp_Rev <- nrow(filter(exp,exp$gamer =='1' & exp$purchase == '1' & exp$gender == "0"))/nrow(filter(exp,exp$gamer =='1'& exp$gender == "0"))*12.5

femalegamer_Cont_Rev
femalegamer_Exp_Rev

```

